### 2018-06-12 express2018/sos.tex
formalization -> formalisation (following title)

In the formalization of CCS, 
the type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' ($\beta$ is a
type variable) accounts for visible actions, divided into input
and output actions:
\begin{lstlisting}
val _ = Datatype `Label = name 'b | coname 'b`;
\end{lstlisting}
Then
the type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' is the
union of all visible and invisible actions. The cardinality of
``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' (and therefore of all
CCS types built on top of it) 
 depends on the choice of initial  type $\beta$.

@@

We have added some  grammar support using HOL's powerful pretty printer, to represent CCS
processes in more readable forms (as shown in the ``HOL (abbrev.)''
column in Table \ref{tab:ccsoperator}, the rest of table has listed the notation of typical CCS processes and
major operators supported by above definition). For restriction
operator, we chose to takes a set of names, rather than a
  single name as in the  CCS syntax, to prevent the formalization
  efforts on the equivalence of CCS processes with different order of
  nested restrictions. Also, we don't assume that al recursion are
  guarded, i.e. any term like \texttt{var X} must appear in \texttt{P} of \texttt{rec X P}.

>>>>

In the formalisation of CCS, 
the type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' ($\beta$ is a
type variable) accounts for visible actions, divided into input
and output actions:
\begin{lstlisting}
val _ = Datatype `Label = name 'b | coname 'b`;
\end{lstlisting}
Then
the type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' is the
union of all visible and invisible actions. The cardinality of
``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' (and therefore of all
CCS types built on top of it) 
 depends on the choice of initial  type $\beta$.

@@

We have added some  grammar support using HOL's powerful pretty printer, to represent CCS
processes in more readable forms (as shown in the ``HOL (abbrev.)''
column in Table \ref{tab:ccsoperator}, the rest of table has listed the notation of typical CCS processes and
major operators supported by above definition). For restriction
operator, we chose to takes a set of names, rather than a
  single name as in the  CCS syntax, to prevent the formalisation
  efforts on the equivalence of CCS processes with different order of
  nested restrictions. Also, we don't assume that al recursion are
  guarded, i.e. any term like \texttt{var X} must appear in \texttt{P} of \texttt{rec X P}.
